The Second Data Release of the INT Photometric H$\alpha$ Survey of the Northern Galactic Plane (IPHAS DR2)

### 2014-07-01 paper/iphas-dr2-rev1.tex
Added GLIMPSE comparison

>>>>

{\bf Moreover, IPHAS provides the much-needed counterpart
to the source catalogues being provided by the recent infrared surveys.
For example, amongst the 1810 high-quality sources considered in Fig.~\ref{fig:emitters},
1623 objects (90\%) have a counterpart in the Spitzer catalogue,
and 371 objects (20\%) have a counterpart in the 
Wide-field Infrared Survey Explorer catalogue (WISE; Cutri et al. 2013),
both within a matching radius of 2 arcsec.}
